business-attributes

### 2016-08-03 eda/business-attributes.Rmd
location data explanation added

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(ggplot2)
library(dplyr)
library(tidyr)
library(magrittr)
library(ggmap)
library(maps)
library(jsonlite)
```

@@

```{r}
us_business <- read.csv('/Users/irenelee/Desktop/SUMMER16/stat133/final_project/clean_data/us-business.csv', stringsAsFactors=FALSE)
noise_level <- read.csv('/Users/irenelee/Desktop/SUMMER16/stat133/final_project/clean_data/noise-attr.csv', stringsAsFactors=FALSE) 
attire_type <- read.csv('/Users/irenelee/Desktop/SUMMER16/stat133/final_project/clean_dta/attire-attr.csv', stringsAsFactors=FALSE)
states <- map_data('state')
ggplot(states) + 
  geom_polygon(aes(x = long, 
                   y = lat, 
                   group = group), 
               fill = "grey80", 
               color = "white") + 
  coord_fixed(1.3) + 
  geom_point(data = us_business, 
             aes(long, 
                 lat, 
                 color = factor(stars), 
                 size = count), 
             alpha = 0.7) + 
  guides(colour = guide_legend("Star Rating"), 
         size = guide_legend("Review Counts")) + 
  labs(title = "Restaurant Reviews in United States") +
  theme_nothing(legend = TRUE)
```

>>>>

```{r packages, include = FALSE}
library(readr)
library(stringr)
library(ggplot2)
library(dplyr)
library(tidyr)
library(magrittr)
library(ggmap)
library(maps)
library(jsonlite)
```

@@

```{r}
us_business <- read_csv('../clean_data/us-business.csv', stringsAsFactors=FALSE)
noise_level <- read_csv('../clean_data/noise-attr.csv', stringsAsFactors=FALSE) 
attire_type <- read_csv('../clean_dta/attire-attr.csv', stringsAsFactors=FALSE)
states <- map_data('state')
ggplot(states) + 
  geom_polygon(aes(x = long, 
                   y = lat, 
                   group = group), 
               fill = "grey80", 
               color = "white") + 
  coord_fixed(1.3) + 
  geom_point(data = us_business, 
             aes(long, 
                 lat, 
                 color = factor(stars), 
                 size = count), 
             alpha = 0.7) + 
  guides(colour = guide_legend("Star Rating"), 
         size = guide_legend("Review Counts")) + 
  labs(title = "Restaurant Reviews in United States") +
  theme_nothing(legend = TRUE)
```
